Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Cleanup inxeding scheme conversion examples

\begin{example}
Consider the following indexing schemes
corresponding to array indexing terms
$(i, j+1)$, $(1, j+1)$, $(3, j)$ and $(i*2, j)$:
%
\begin{align*}
\begin{array}{ll}
\schemeN{(i, j+1)} & =\vtwoh{0}{1} \\
\schemeN{(1, j+1)} & = \vtwoh{\infty}{1} \\
\schemeN{(3, j)} & = \vtwoh{\infty}{0} \\
\schemeN{(i*2, j)} & = \bot
\end{array}
\end{align*}
There is one generalisation between these
schemes, namely that $\vtwoh{0}{1} \preceq_2 \vtwoh{\infty}{1}$.
Note the last example is undefined as its first expression is a
non-neighbour relative index.
\end{example}

>>>>

\begin{example}
Consider the following array subscript to indexing schemes
conversions:
%
\begin{align*}
\begin{array}{ll}
\schemeN{(i, j+1)} & =\vtwoh{0}{1} \\
\schemeN{(1, j+1)} & = \vtwoh{\infty}{1} \\
\schemeN{(3, j)} & = \vtwoh{\infty}{0} \\
\schemeN{(i*2, j)} & = \bot
\end{array}
\end{align*}
There is one generalisation between these
schemes, namely that $\vtwoh{0}{1} \preceq_2 \vtwoh{\infty}{1}$.
The last example is undefined as its first expression is a
non-neighbour relative index.
\end{example}
